MSE Scenarios for short and long lived

### 2025-04-15 Scenarios.Rmd
update recsig, mean_rec_par in base

# Set sigma for NAA
NAA_sig <- 0.2
sigma_vals = array(NAA_sig, dim = c(n_stocks, n_regions, n_ages)) # n_stocks x n_regions x n_ages"

@@

NAA_re <- list(N1_model=rep(ini.opt,n_stocks),
               sigma=rep(sigma,n_stocks),
               cor=rep(re_cor,n_stocks),
               recruit_model = 2,
               #recruit_pars = rep(list(c(alpha,beta)),n_stocks), # assume same B-H s-r functions for all stocks
               sigma_vals = sigma_vals,
               N1_pars = N1_pars)#,
               #NAA_where = basic_info$NAA_where)

>>>>

# Set sigma for NAA
# add higher rec_sig similar to redfish WHAM
rec_sig <- 1.0
NAA_sig <- 0.2
sigma_vals = array(NAA_sig, dim = c(n_stocks, n_regions, n_ages)) # n_stocks x n_regions x n_ages"
sigma_vals[,,1] = Rec_sig

@@

# Set mean recruitment para. for each stock
mean_rec_par <- list()
for (i in 1:n_stocks) mean_rec_par[[i]] <- exp(log_N1[i])

NAA_re <- list(N1_model=rep(ini.opt,n_stocks),
               sigma=rep(sigma,n_stocks),
               cor=rep(re_cor,n_stocks),
               recruit_model = 2,
               recruit_pars = mean_rec_par, # rep(list(c(alpha,beta)),n_stocks), # assume same B-H s-r functions for all stocks
               sigma_vals = sigma_vals,
               N1_pars = N1_pars)#,
               #NAA_where = basic_info$NAA_where)
